A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-21 paper.tex
reduce to 9 pages

CMSSW contains many different tools, libraries, and utilities.  No single code uses anywhere close to all of these.  But, because it is widely used within the experimental researchers, it is common for users and developers to simply expect that a particular version of the entire repository is available.

@@

Parrot is a virtual filesystem access tool which has previously been used to attach
existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
It works by trapping an application's system calls through the {\tt ptrace} debugging
interface, and then replacing them with the desired I/O operations.  Parrot is already used
in the high energy physics community with applications like TauRoast specifically to 
provide access to the CMSSW software distribution via the CVMFS distributed file system.
We made small modifications to Parrot to record a \emph{namelist} which lists all 
of the files that an application actually accesses.

@@

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the archive that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
instead of ingested. A researcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.

@@

{\bf Granularity of Dependencies.}  Dependencies could be handled
at many different levels of granularity.  In this work, we have shown
how they can be handled at the level of entire repositories or individual files.
Other possible choices might include intermediate-sized software packages
(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in fewer packages,
simpler dependency maps, and more wasted space; smaller granularity results
in complex dependency maps and less wasted space.  A hybrid solution may
be able to combine both by storing large granularity dependencies, but
retain the ability to select sub-items out of objects when efficiency demands it.

@@

{\bf Dependency Detection.}  If we allow users to work in uncontrolled
environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
the user's script and extract the repository dependencies.  This is clearly
not a scalable approach.  We then demonstrated an automated method of observing
what individual files are accessed by a program. However, this does
not cover all types of dependencies, particularly those that are networked.
More sophisticated observation techniques could infer higher-level information,
such as the RPM package names of the files accessed, the URLs of remote
repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.

@@

The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.

@@

Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments. However, this is not always right. In some cases, the original author may leave additional code referring to irrelative data and software in the experiment programs. One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.

B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future, including type, purpose, new users.
To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.

>>>>

CMSSW contains many different tools, libraries, and utilities.  No single code uses anywhere close to all of these.  But, because it is widely used within the experimental researchers, it is common for users to simply expect that a particular version of the entire repository is available.

@@

Parrot is a virtual filesystem access tool which has been used to attach
existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
It works by trapping an application's system calls through the {\tt ptrace} debugging
interface, and then replacing them with the desired I/O operations.  Parrot is already used
in the high energy physics community with applications like TauRoast specifically to 
provide access to the CMSSW software distribution via the CVMFS distributed file system.
We made small modifications to Parrot to record a \emph{namelist} which lists all 
of the files that an application actually accesses.

@@

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the archive that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
. A researcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.

@@

{\bf Granularity of Dependencies.}  Dependencies could be handled
at many different levels of granularity.  In this work, we have shown
how they can be handled at the level of entire repositories or individual files.
Other possible choices might include intermediate-sized software packages
(like RPM) or in the case of experimental data, even portions of individual large files.  Clearly, a larger granularity will result in 
simpler dependency maps, and more wasted space; smaller granularity results
in complex dependency maps and less wasted space.  A hybrid solution may
be able to combine both by storing large granularity dependencies, but
selecting sub-items out of objects when efficiency demands it.

@@

{\bf Dependency Detection.}  If we allow users to work in uncontrolled
environments, then we must have better methods for understanding the dependencies  of existing programs.  At first, we relied on an expert reader to examine
the user's script and extract the dependencies.  This is clearly
not a scalable approach.  We then demonstrated an automated method of observing
what individual files are accessed by a program. However, this does
not cover all types of dependencies, particularly those that are networked.
More sophisticated observation techniques could infer higher-level information,
such as the RPM package names of the files accessed, the URLs of remote
repositories named throughout the program, or even the addresses and names of networked dependencies like databases and filesystems.

@@

The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid the time-consuming software building procedure.

@@

Current mechanisms of preserving scientific experiments assume that all the data and software mentioned in the experiments are necessary for the reproduction of the experiments. However, this is not always right. In some cases, the original author may leave additional code referring to irrelative data and software in the program. One mechanism, which can figure out the absolutely relevant data and software of one experiment, is important for both the preservation and reproduction of scientific experiments.

B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future.
To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.
